>

### 2025-03-12 docs/supplementary.qmd
Restructure the supplementary file

@@

@@

>>>>

---
title: >
  Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022

format:
  pdf:
    keep-tex: false
    include-in-header:
      - file: _header.tex
      - text: |
          \renewcommand*{\thesection}{S\arabic{section}}
    output-file: iadb-network-analysis-supplementary.pdf
    number-sections: true
    number-depth: 3
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis-supplementary.docx

metadata-files:
  - _author.yml
  - _knitr-bib.yml

in:
  article: true
---

@@

# Methods

## Decomposition with singular spectrum analysis

{{< include exec-summary/_spectral.qmd >}}

# Results

## Cyclical patterns on de-trended data

@@

# References {-}
